\section{What is this book?}
This is a book of everything that I've learned throughout my college journey; from taking
prerequisites all the way to the final course before graduation.
\subsection{Why?}
Over 4 years, I have accrued over \$30 thousand dollars in debt, had many sleepless nights,
went through a break-up (probably in part due to school), and struggled financially for most of it.
Beyond just a piece of paper I paid a lot of money for, I figured what better way
to visually see everything I've gone through?

Actually, I'm somewhat lying, the
idea came from a book that I read called
\textit{"Surely You're Joking, Mr. Feynman!"} Adventures of a Curious Character%
\footnote{Richard P. Feynman and Ralph Leighton,
\textit{“Surely You're Joking, Mr. Feynman!”: Adventures of a Curious Character},
W. W. Norton \& Company, 1985.}. Well, technically not from the actual book, but
from the guy who wrote it, Dr. Richard Feynman. There is a quote by him that reads
"What I cannot create, I do not understand" and from it, the Feynman Technique was created.

The idea is simple: \textbf{if you can’t explain something to a five-year-old, you don’t really understand it.}
So, dear reader—you are my five-year-olds. I hope you understand everything I’m about to say.

As I write this, it is October 20th, 2025 - 4-ish years since I took that first
College Algebra course. Since I am starting this so late, this means I have to
chase down old notes, decipher my god awful handwriting, and try to put it into
words that actually make sense. Because of this, there will inevitably be large
chunks of courses missing. That's okay, because this isn't as much about the content,
but my journey through it.


\subsection{Who is this for?}
I don't know, maybe no one. It's not an attempt to tell a story, it's to share my
experiences. This means that there could be sections that should be read by family,
sections that should be read by professors, or maybe even sections I should re-read.
I don't ever plan on selling this, maybe just making a few copies to give to those
that mean the most to me. If you're reading this, you've probably stumbled upon it
at a yard sale, or you're one of those people who mean the most to me. I did pay
to get this made with my hard-earned Computer Science degree, you know.

\subsubsection{For my Mom}
Since it seems to be an "unwritten rule" to dedicate a book to someone, I dedicate
this to my Mom. On April 18, 2021, she watched her only son leave to travel 1,688 miles
away to Austin, Texas. She never told me no or that I should think about it; she actually
encouraged me to go. She knew that I wouldn't go otherwise.

I know that it crushed her,
but I think she knew deep down that this is what I needed. Since then, she has spent countless
hours on the phone with me listening to me vent about school. She has been my rock and
will forever be the reason I am the person I am today.

I am grateful for her beyond just school, but for everything that I have accomplished
because of it. Without her, I would never have left. So yeah, I think that she deserves
more than just a paragraph in a book of MY life.
